\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-14 paper/ms.tex
A bit more writing

\section{Bayesian computation and Nested Sampling}

Bayesian inference, where probability theory is used to describe degrees of
logical implication or subjective certainty, provides a powerful general basis
for data analysis \citep{ohagan, sivia}. The result of such
an analysis is typically
posterior probabilities of various hypotheses, or (more specifically)
a joint posterior probability distribution for the values of unknown
parameters.

@@

\subsection{Markov Chain Monte Carlo}
DNS is build upon the Metropolis-Hastings algorithm.
In this algorithm, the acceptance probability $\alpha$
is given by
\begin{align}
\alpha &= \min\left(1,
\frac{q(\params'|\params)}{q(\params | \params')}
\frac{\pi(\params')}{\pi(\params)}\frac{L(\params')}{L(\params)}
\right)
\end{align}
where $q(\theta' | \theta)$ is the proposal distribution used to generate
a new position $\theta'$ from the current position $\theta$. Often,
$q$ is {\em symmetric} so the $q$ terms cancel in the acceptance probability.

@@

\section{Dependencies and installation}

@@

\section{Advanced usage}

@@

\section{Implementing models}
The ``classic'' method of implementing models in \pkg{DNest4} is by
writing a \proglang{C++} class, an object of which represents a
point in your parameter space.
To demonstrate, consider a simple linear regression situation where the
sampling distribution is
\begin{align}
y_i | m, b, \sigma &\sim \textnormal{Normal}(mx_i + b, \sigma^2)
\end{align}
and the priors are
\begin{align}
m &\sim \textnormal{Normal}(0, 1000^2)\\
b &\sim \textnormal{Normal}(0, 1000^2)\\
\ln\sigma &\sim \textnormal{Uniform}(-10, 10)
\end{align}
These are naive diffuse priors and we do not claim any special status for them.

@@

>>>>

\section{Introduction}
Bayesian inference, where probability theory is used to describe degrees of
logical implication or subjective certainty, provides a powerful general basis
for data analysis \citep{ohagan, sivia}. The result of such
an analysis is typically
posterior probabilities of various hypotheses, or (more specifically)
a joint posterior probability distribution for the values of unknown
parameters.

@@

There are several ways of using \pkg{DNest4}. After installing the software
(Section~\ref{sec:installation}), you can implement a model in \proglang{C++}
(Section~\ref{sec:models}) and compile it to create an executable file
to run \pkg{DNest4} on that problem. This method offers the flexibility

\section{Markov Chain Monte Carlo}\label{sec:mcmc}
DNS is build upon the Metropolis-Hastings algorithm.
In this algorithm, the acceptance probability $\alpha$
is given by
\begin{align}
\alpha &= \min\left(1,
\frac{q(\params'|\params)}{q(\params | \params')}
\frac{\pi(\params')}{\pi(\params)}\frac{L(\params')}{L(\params)}
\right)
\end{align}
where $q(\theta' | \theta)$ is the proposal distribution used to generate
a new position $\theta'$ from the current position $\theta$. Often,
$q$ is {\em symmetric} so the $q$ terms cancel in the acceptance probability.

@@

\section{Dependencies and installation}\label{sec:installation}

@@

@@

\section{Implementing models}\label{sec:models}
The ``classic'' method of implementing models in \pkg{DNest4} is by
writing a \proglang{C++} class, an object of which represents a
point in your parameter space.
To demonstrate, consider a simple linear regression situation where the
sampling distribution is
\begin{align}
y_i | m, b, \sigma &\sim \textnormal{Normal}(mx_i + b, \sigma^2)
\end{align}
and the priors are
\begin{align}
m &\sim \textnormal{Normal}(0, 1000^2)\\
b &\sim \textnormal{Normal}(0, 1000^2)\\
\ln\sigma &\sim \textnormal{Uniform}(-10, 10)
\end{align}
These are naive diffuse priors and we do not claim any special status for them.

@@

\subsection{Python Bindings}
